---
title: "Chapter 3 - Functions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Creating your own functions:

In general:

```{r}
my_fun <- function(arg1, arg2) {
  body
}
```

Examples:

```{r}
# Create a function pow_two()
pow_two <- function(x) {
    x^2
}


# Use the function
pow_two(12)

# Create a function sum_abs()
sum_abs <- function(x,y){
    sum(abs(x)+abs(y))
}


# Use the function
sum_abs(-2,3)
```


Can write functions that do not require any input:
```{r}
throw_die <- function() {
  number <- sample(1:6, size = 1)
  number
}

throw_die()
```

Example: 


```{r}
# Define the function hello()
hello <- function(){
    print("Hi there!")
    return(TRUE)
}




# Call the function hello()
hello()
```

Can also add in optional arguments:
```{r}
# Finish the pow_two() function
pow_two <- function(x, print_info=TRUE) {
  y <- x ^ 2
  if(print_info==TRUE){
    print(paste(x, "to the power two equals", y))
  }
  return(y)

  
}


pow_two(20)
```

two_dice <- function() {
  possibilities <- 1:6
  dice1 <- sample(possibilities, size = 1)
  dice2 <- sample(possibilities, size = 1)
  dice1 + dice2
}

two_dice()


## R passes arguments by value:


The title gives it away already: R passes arguments by value. What does this mean? Simply put, it means that an R function cannot change the variable that you input to that function. Let's look at a simple example (try it in the console):




```{r}

triple <- function(x) {
  x <- 3*x
  x
}
a <- 5
triple(a)
a
```

```{r}

# The linkedin and facebook vectors have already been created for you


facebook <- c(17,7,5,16,8,13,14)
facebook

linkedin <- c(16,9,13,5,2,17,14)
linkedin

# Define the interpret function
interpret <- function(num_views) {
  if (num_views > 15) {
    print("You're popular!")
    return(num_views)

  } else {
    print("Try to be more visible!")
    return(0)

  }
}

# Call the interpret function twice for specific indices
interpret(linkedin[1])

interpret(facebook[2])

```

## Adding in a for loop

Here we start to add some for loops

```{r}

# The linkedin and facebook vectors have already been created for you
linkedin <- c(16, 9, 13, 5, 2, 17, 14)
facebook <- c(17, 7, 5, 16, 8, 13, 14)

# The interpret() can be used inside interpret_all()
interpret <- function(num_views) {
  if (num_views > 15) {
    print("You're popular!")
    return(num_views)
  } else {
    print("Try to be more visible!")
    return(0)
  }
}

# Define the interpret_all() function
# views: vector with data to interpret
# return_sum: return total number of views on popular days?
interpret_all <- function(views, return_sum=TRUE) {
  count <- 0

  for (v in views) {
    count<- count+ interpret(v)
  }

  if (return_sum== TRUE) {
  return(count)   
  } else {
NULL
  }
}

# Call the interpret_all() function on both linkedin and facebook

interpret_all(facebook)

interpret_all(linkedin)


```
this is a test


test again